\newcommand\jobtitle[2]{
	\subsubsection*{\textbf#1\hfill\normalfont#2}
}

\newcommand\position[5]{
	\subsection*{#1\hfill#2}
	\jobtitle{#3}{#4}
	#5
	\vspace{-0.25cm}
}

\mainsection{Work Experience}

\position{Clarity RFID}{Plano, TX}{Senior Software Engineer}{April 2024 - Present}{
	\begin{itemize}
		\item Led development of a SaaS web application platform encompassing reporting, workflow management, and admin tooling, mentoring developers and driving architectural decisions projected to reduce customer on-boarding time by 25\%.
		\item Designed and implemented a high-precision item-tracking system using Geographic Information Systems (GIS) to map RFID read locations, achieving 94\% location accuracy, directly improving loss prevention outcomes.
		\item Served as a major contributor on the architectural rewrite of the core mobile application from Xamarin to .NET MAUI, improving navigation, app loading, build times, and overall performance.
	\end{itemize}

	\jobtitle{Software Engineer II}{April 2022 - April 2024}
	\begin{itemize}
		\item Led development of a retail web application deployed across 30+ enterprise customers, delivering real-time metrics and reporting built with TypeScript, SvelteKit, and TailwindCSS.
		\item Contributed to the development of a new supply chain platform serving 10 enterprise customers, designing microservices to handle customer-driven auditing and business logic built with .NET Aspire, C\#, PostgreSQL, Docker, and Kubernetes.
		\item Engineered system-wide ETL integrations to ingest and map customer data across a variety of transfer mechanisms including Azure Service Bus, Kafka, and FTP.
	\end{itemize}

	\jobtitle{Software Engineer}{December 2020 - April 2022}
	\begin{itemize}
		\item Designed and implemented RESTful APIs and automated background jobs in C\#, SQL Server, and Redis to power item-level RFID tagging features across retail inventory workflows.
		\item Developed native mobile applications with Xamarin Forms integrated with RFID hardware, enabling real-time inventory management for retail staff.
	\end{itemize}
}

\position{Game Grumps}{Remote}{Contract Software Engineer}{May 2022 - Sep 2022}{
	\begin{itemize}
		\item Co-led migration of merchandise store from Shopify Hydrogen to Next.js, improving page load performance, SEO rankings, and user experience, resulting in a 250\% increase in merchandise revenue within 3 months of launch.
		\item Engineered custom CMS integrated with Shopify Admin API and GraphQL to enable real-time product synchronization, inventory management, and dynamic filtering. 
	\end{itemize}
}

\position{Dallas Baptist University}{Dallas, TX}{Network \& System Administrator}{Mar 2017 - Dec 2020}{
	\begin{itemize}
		\item Developed an open-source Python network automation tool managing 60+ network switches, replacing manual processes for port security, SNMP, configuration, and report generation.
		\item Deployed and managed network infrastructure for 4,000+ users across three campuses, maintaining high network speed and stable/secure network connectivity.
		\item Enhanced web application security by migrating from insecure credentials to Azure password-less authentication using Managed Service Identity (MSI) and Azure Key Vault.
	\end{itemize}
}

